Earth's Impact History and the Timing of the Origin of Life

### 2023-04-14 ms.tex
introduction draft done

% Title
\title{Earth's Impact History and the Timing of the Origin of Life}
\author{Nicholas F. Wogan}
\affiliation{Department of Earth and Space Sciences, University of Washington, Seattle, WA 98195}
\affiliation{Virtual Planetary Laboratory, University of Washington, Seattle, WA98195}

@@

Recently, \citep{Wogan_2023} considered life-starting impactors significantly smaller than Moneta

>>>>

% Title
\title{Earth's Impact History and the Timing of the Origin of Life}

% Authors
\author{Nicholas F. Wogan}
\affiliation{Department of Earth and Space Sciences, University of Washington, Seattle, WA 98195}
\affiliation{Virtual Planetary Laboratory, University of Washington, Seattle, WA98195}

@@

Recently, \citep{Wogan_2023} use photochemical models of post-impact atmospheres to show that impacts significantly smaller than Moneta should efficiently produce prebiotic molecules. In an optimistic modeling case, a $> 4 \times 10^{20}$ kg impact produces atmosphere that generates copious prebiotic molecules, while in their most pessimistic scenario a $> 5 \times 10^{21}$ kg impactor is required. It is therefore possible that an impactor much smaller than Moneta caused the origin of life, and that the \citet{Benner_2020} estimated timing for biopoesis, based on Moneta starting life, could be inaccurate.

Here, we use the \citep{Wogan_2023} results, along with Monte-Carlo simulations of Earth's impact history to make an alternative estimate for when life most likely emerged during an RNA-first process.
